Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2018-11-23 man/figures/browning.Rmd
adjust size

---
output: 
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    highlight: null
    reference_docx: ../../templates/template_pagebreak.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
editor_options: 
  chunk_output_type: console
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE, dpi = 200)
```

```{r}
library("tidyverse")
library("here")
library("dplyr")
library("ggrepel")
library("scales")

library("grid")
library("gridExtra")
library("patchwork")
library("ggcorrplot")
library("stringr")
library("pander")
library("lemon")
library("viridis")
library("ggthemes")
```

```{r, echo=FALSE}
show_text <- FALSE
```
##### 
**Appendix S4.** Percentage of pixels showing browning, greenning or no-changes during the 2005 and 2012 droguht events according to EVI standardized anomalies.

```{r}
df <- read.csv(file=here::here('/out/anomalies/evi' ,'percen_browing_greening.csv'), header=TRUE)

@@

df <- df %>% mutate(type = stringr::str_to_title(type))

per_pixels_green <- df %>% 
  ggplot(aes(x=type, y=per, fill=as.factor(y))) + 
  geom_bar(stat='identity', position = "dodge") + 
  # geom_text(aes(label = paste0(per, " %")), position=position_dodge(width=0.9), hjust=-.1, size=3, angle = 90) + 
  facet_wrap(~clu_pop2) + 
  theme_bw() + xlab('') + ylab('Frequency of pixels (%)') +
  theme(strip.background = element_rect(colour = "black", fill = "white")
        ) + labs(fill = 'Drought event') + scale_fill_manual(values = c("#DAA520", "#104E8B")) +
  scale_y_continuous(expand=c(.1,0)) + 
  geom_text_repel(aes(label = paste0(per, " %")), 
                  position=position_dodge(width=0.9))

per_pixels_green
```

>>>>

---
output:
  word_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE)
```

```{r load_pkg}
library("tidyverse")
library("here")
library("scales")
library("viridis") # colours 
library("ggthemes") # colours 
```

#####

**Figure 3.** Percentage of pixels showing browning, greenning or no-changes during the 2005 and 2012 drought events according to EVI standardized anomalies.

```{r data}
df <- read.csv(file=here::here('/out/anomalies/evi' ,'percen_browing_greening.csv'), header=TRUE)

@@

df <- df %>% mutate(type = stringr::str_to_title(type))
```

```{r plot}
per_pixels_green <- df %>% 
  ggplot(aes(x=type, y=per, fill=as.factor(y))) + 
  geom_bar(stat = 'identity', position = "dodge") + 
  geom_text(aes(label = paste0(per, " %")), position=position_dodge(width=0.9), hjust=-.1, size=2, angle = 90) + 
  facet_wrap(~clu_pop2) + 
  theme_bw() + xlab('') + ylab('Frequency of pixels (%)') +
  theme(strip.background = element_rect(colour = "white", fill = "white"),
        strip.text = element_text(size = 8), 
        axis.title.y = element_text(size = 10, face = 'bold'),
        axis.text = element_text(size = 8),
        panel.grid = element_blank(),
        legend.position = 'bottom') + 
  labs(fill = 'Drought event') + 
  scale_fill_colorblind() + 
  scale_y_continuous(limits = c(0, 110), breaks = c(0, 25, 50, 75, 100))
```

```{r out_plot, fig.width= 4, dpi = 300, out.width = 0.8}
per_pixels_green
```
